Exercise 3: Software Architecture in Practice Case: Beer Web Store

### 2008-03-17 trunk/SAiP/Module1/H3/doc/architecturaldescription.tex
Fixing c in facade

Figure \ref{fig:ad_package} shows a package diagram of the Beer Web
Store and a decomposition of the web package. The Web package
contains the elements used for the web interface, 
the Overview page, the basket and the domain model. The domain model
depends on a Database package that contains the database fa\c ade and the
database fa\c ade uses some database package library, e.g. MySQL.

@@

The domain model accesses the database through the database fa\c ade
when needed. This can be expressed in another sequence diagram.
Sequence diagrams showing the checkout including payment must
also be made.

@@

The application code (Beer Web) and the database fa\c ade are
both deployed on the web server.

>>>>

Figure \ref{fig:ad_package} shows a package diagram of the Beer Web
Store and a decomposition of the web package. The Web package
contains the elements used for the web interface, 
the Overview page, the basket and the domain model. The domain model
depends on a Database package that contains the database fa\c cade and the
database fa\c cade uses some database package library, e.g. MySQL.

@@

The domain model accesses the database through the database fa\c cade
when needed. This can be expressed in another sequence diagram.
Sequence diagrams showing the checkout including payment must
also be made.

@@

The application code (Beer Web) and the database fa\c cade are
both deployed on the web server.
